results

### 2020-12-17 analysis/results.Rmd
tmp save

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
  "Articles published", "articles_n", "Total",
  "Articles published", "articles_mean", "Avg.",
  "Articles published", "articles_sd", "SD",
  "of which OA", "oa_n", "Total ",
  "of which OA", "oa_mean", "Avg.",
  "of which OA", "oa_sd", "SD",
  "OA Uptake (in%)", "oa_uptake", "Percentage",
  "OA Uptake (in%)", "oa_uptake_mean", "Avg.",
  "OA Uptake (in%)", "oa_uptake_sd", "SD",
  "Elsevier Hybrid Journals with OA article(s)", "n_journals", "Journals"
)
gt_1 <- inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20"), decimals = 1) %>%
  fmt_number(contains("20"), 
             rows = c("Total", "Total ", "Journals"),
             decimals = 0) %>%
  tab_style(
    style = cell_fill(
      color = "grey90"
    ),
    locations = list(
      cells_body(
        columns = "2015-19"
      ),
      cells_column_labels(
        columns = "2015-19"
      )
    )
  ) %>%
  tab_style(
    style = cell_text(color = "black", weight = "bold"),
    locations = list(
      cells_column_labels(everything())
    )
  )  %>%
   tab_style(
    style = cell_text(color = "black", style = "italic"),
    locations = list(
      cells_row_groups())
    ) %>%
  cols_width(
    2 ~ px(125),
    3:7 ~ px(80),
    8 ~ px(110)
  ) %>%
  tab_options(
    row_group.border.top.width = px(3),
    row_group.border.top.color = "white",
    row_group.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.top.color = "white",
    table.border.top.width = px(3),
    table.border.bottom.color = "white",
    table.border.bottom.width = px(3),
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width = px(2),
    stub.border.color = "white"
  )
gt_1
```

@@

```{r, fig.cap = "Open access uptake per Elsevier hybrid journal in percent by year, visualized as box-and-whiskers plot. The Y-axis is limited to an open access share of 18%."}
hybrid_oa_volume %>%
  mutate(prop = oa / articles) %>%
  filter(oa > 0) %>%
ggplot(aes(factor(issued_year), prop)) + 
  geom_boxplot(outlier.size = 1, outlier.alpha = .5) + 
  coord_cartesian(ylim=c(0,0.2)) +
  theme_minimal_hgrid() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L),
      expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Publication Years",
       y = "Open Access Uptake")
```

@@

license_df %>%
  group_by(type, license_code) %>%
  summarise(n = sum(articles)) %>%
  mutate(prop = n / sum(n))
```

@@

@@

```{r invoiceoverview, fig.cap="Development of fee-based open access publishing in Elsevier hybrid journals by invoicing type. Colored bars represent the invoice recipient, or whether the fee was waived. Grey bars show the total number of hybrid open access articles published in Elsevier journals from 2015 to date."}
# plot
ggplot(sponsored_articles, aes(x = gsub("20", "'", issued_year), y = n), alpha = 0.8) +
  geom_bar(
    data = all_articles,
    color = "transparent",
    stat = "identity",
    fill = "#b3b3b3a0"
  ) +
  geom_bar(aes(fill = cc_norm), color = "white", stat = "identity", alpha = 0.8, size = 0.25,
           position = position_stack(reverse = T)) +
  facet_wrap( ~ fct_source, nrow = 1) +
  scale_fill_manual(values = 
                      c(`cc-by` = "#B52141",
                        `cc-by-nc-nd` = "#0093c7"),
                    name = "CC license variant") +
  labs(x = NULL, y = NULL) + 
  scale_y_continuous(labels = scales::number_format(big.mark = " "),
                      expand = expansion(mult = c(0, 0.05))) + theme_minimal_hgrid() +
  theme(legend.position="top", legend.justification = "right")
```

@@

@@

@@

```{r}
p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y") +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Years OA Uptake Rate per Journal") +
  theme_minimal_vgrid(font_size = 10) 
ggsave(here::here("figure", "subject_by_area.png"), p_subject, dpi = 300, width = 8, height = 6)
p_subject
```

@@

```{r}
ggplot(hybrid_subject_19, aes(prop, snip)) + geom_point(alpha = 0.2) + 
  geom_smooth(method = "loess", se = TRUE) +
  coord_cartesian(xlim = c(0., 0.7), ylim = c(0.5, 6)) +
  labs(x = "OA Uptake Rate", y = "SNIP") +
  theme_cowplot()
```

>>>>

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
    "Elsevier Hybrid Journals with ≥ 1 OA article", "n_journals", "All (n)",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "articles_n", "All (n) ",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "articles_mean", "Avg.",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "articles_sd", "SD",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_n", "OA (n)",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_mean", "Avg.",
  "Articles in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_sd", "SD",
  "OA Uptake in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_uptake", "Total (%)",
  "OA Uptake in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_uptake_mean", "Avg.",
  "OA Uptake in Elsevier Hybrid Journals with ≥ 1 OA article", "oa_uptake_sd", "SD"
)
gt_1 <- inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20"), decimals = 1) %>%
  fmt_number(contains("20"), 
             rows = c("All (n)", "All (n) ", "OA (n)"),
             decimals = 0) %>%
  tab_style(
    style = cell_fill(
      color = "grey90"
    ),
    locations = list(
      cells_body(
        columns = "2015-19"
      ),
      cells_column_labels(
        columns = "2015-19"
      )
    )
  ) %>%
  tab_style(
    style = 
      cell_text(weight = "bold"),
    locations = cells_stub(c("All (n)", "All (n) ", "OA (n)", "Total (%)"))) %>%
  tab_style(
    style = cell_text(color = "black", weight = "bold"),
    locations = list(
      cells_column_labels(everything())
    )
  )  %>%
   tab_style(
    style = cell_text(color = "black", style = "italic"),
    locations = list(
      cells_row_groups())
    ) %>%
  cols_width(
    2 ~ px(125),
    3:7 ~ px(80),
    8 ~ px(110)
  ) %>%
  tab_options(
    row_group.border.top.width = px(3),
    row_group.border.top.color = "white",
    row_group.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.top.color = "white",
    table.border.top.width = px(3),
    table.border.bottom.color = "white",
    table.border.bottom.width = px(3),
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width = px(2),
    stub.border.color = "white"
  )
gt_1
gt::gtsave(gt_1, here::here("figure","gt_overview.png"))

@@

```{r, fig.cap = "Open access uptake per Elsevier hybrid journal in percent by year, visualized as box-and-whiskers plot. The Y-axis is limited to an open access share of 18%."}
hybrid_oa_volume %>%
  mutate(prop = oa / articles) %>%
  filter(oa > 0) %>%
ggplot(aes(factor(issued_year), prop)) + 
  geom_boxplot(outlier.size = 1, outlier.alpha = .5) + 
  coord_cartesian(ylim=c(0,0.2)) +
  theme_minimal_hgrid() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 5L),
      expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Publication Year",
       y = "Hybrid OA Uptake")
```

@@

license_df %>%
  group_by(type, license_code) %>%
  summarise(n = sum(articles)) %>%
  mutate(prop = n / sum(n))
all_oa <- license_df %>% 
  group_by(type) %>% 
  summarise(n = sum(articles)) %>%
  pull(n) %>%
  sum()
all_oa
```

@@

```{r}
sponsored_articles %>% 
  group_by(fct_source) %>% 
  summarise(nn = sum(n)) %>% 
  mutate(cumsum = cumsum(nn)) %>% 
  mutate(prop = nn / sum(nn) * 100) %>%
  mutate(cumprop = cumsum(prop)) %>%
  adorn_totals("row") %>%
  knitr::kable(digits = 1)
```

@@

```{r invoiceoverview, fig.cap="Development of fee-based open access publishing in Elsevier hybrid journals by invoicing type. Colored bars represent the invoice recipient, or whether the fee was waived. Grey bars show the total number of hybrid open access articles published in Elsevier journals from 2015 to date."}
# plot
ggplot(sponsored_articles, aes(x = gsub("20", "'", issued_year), y = n), alpha = 0.8) +
  geom_bar(
    data = all_articles,
    color = "transparent",
    stat = "identity",
    fill = "#b3b3b3a0"
  ) +
  geom_bar(aes(fill = cc_norm), color = "white", stat = "identity", alpha = 0.8, size = 0.25,
           position = position_stack(reverse = T)) +
  facet_wrap( ~ fct_source, nrow = 1) +
  scale_fill_manual(values = 
                      c(`cc-by` = "#B52141",
                        `cc-by-nc-nd` = "#0093c7"),
                    name = "CC license variant") +
  labs(x = "Publication year", y = "Hybrid OA Articles") + 
  scale_y_continuous( 
                     labels = scales::number_format(big.mark = " "),
                      expand = expansion(mult = c(0, 0.05))) +
  theme_minimal_hgrid() +
  theme(legend.position="top", legend.justification = "right")
```

@@

```{r}
hybrid_invoice <-hybrid_volume %>%
  filter(oa_sponsor_type == "FundingBody") %>%
 # rename(yrl_volume = articles) %>%
  left_join(tt, by = c("oa_sponsor_name")) %>%
  mutate(cc_norm = ifelse(grepl("/by/", URL), "cc-by", "cc-by-nc-nd"))

sponsor_country_t <- hybrid_invoice %>%
  # manual changes
  mutate(Country = ifelse(grepl("European|CERN", oa_sponsor_name), "EU", Country)) %>%
  mutate(Country = ifelse(Country == "Multinational", "Other", Country)) %>%
  mutate(Country = ifelse(is.na(Country), "Other", Country)) %>%
  mutate(country_factor = fct_lump(Country, prop = 0.025)) %>%
  mutate(country_factor = fct_infreq(country_factor)) %>%
  mutate(country_factor = fct_relevel(country_factor, "Other", after = Inf))

sponsor_country_t %>%
  count(issued_year, Sector, country_factor, cc_norm) %>%
  ggplot(aes(issued_year, n, fill = Sector)) + 
  geom_bar(stat = "identity") +
  facet_wrap(~country_factor)
```

@@

```{r}
sponsor_country %>%
  group_by(country_factor) %>%
  summarise(nn = sum(n)) %>%
  mutate(prop = nn / sum(nn))
```

@@

```{r}
p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y") +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Years Hybrid OA Uptake Rate per Journal") +
  theme_minimal_vgrid(font_size = 10) 
ggsave(here::here("figure", "subject_by_area.png"), p_subject, dpi = 300, width = 8, height = 6)
p_subject
```

@@

```{r}
ggplot(hybrid_subject_19, aes(prop, snip)) + geom_point(alpha = 0.2) + 
  geom_smooth(method = "loess", se = TRUE) +
  coord_cartesian(xlim = c(0., 0.7), ylim = c(0.5, 6)) +
  labs(x = "Hybrid OA Uptake", y = "SNIP") +
  theme_cowplot()
```
